The Exoplanet Orbit Database \textsc{II}: 2014 updates

### 2014-03-19 draft/ms.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
The Exoplanet Orbit Database (EOD) collects orbital and stellar parameters of all known exoplanets reported in the peer-reviewed literature. The EOD can be navigated through the Exoplanet Data Explorer (EDE) Plotter and Table, available at exoplanets.org. We have ZZZ number of confirmed exoplanets as of March 2014. 
Since \cite{Wright2011}, we made an effort to put robustly detected exoplanets together with over 3000 sample of exoplanet candidates (\kepler\ Objects of Interest, KOIs) and other planets (the ones detected by microlensing, imaging, timing) on exoplanets.org. We also added some new fields (e.g. the secondary eclipse depths), removed obsolete fields, and revised some fields as necessary.

@@

@@

%------------------------------------------------------------------------------
% Figure: single planet page
\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../fig/mass-per-color.eps}
\caption{An example plot produced by the interactive plotting tools of
  EDE on exoplanets.org. The $x$-axis is planet orbital period in days
  and $y$-axis is planet mass in Earth's mass. The exoplanet samples
  being plotted are the ones in the EOD, including transit planets
  (blue large dots), RV planets (red triangles), and timing planets
  (magenta squares). The KOIs are plotted as black small dots, and
  their masses are calculated using their radii based on mass-radius
  relations from the literature (see Section~\ref{sec:orbit}).}
\label{fig:koi}
\end{figure}

ZZZ orbital mass vs orbital distance

ZZZ screen shots of what it looks like in the browser

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

The Exoplanet Orbit Database (EOD) collects orbital and stellar
parameters of all known exoplanets reported in the peer-reviewed
literature. The EOD can be navigated through the Exoplanet Data
Explorer (EDE) Plotter and Table, available at exoplanets.org. We have
ZZZ number of confirmed exoplanets as of March 2014.  
Since \cite{Wright2011}, we made an effort to put robustly detected
exoplanets together with over 3000 sample of exoplanet candidates
(\kepler\ Objects of Interest, KOIs) and other planets (the ones
detected by microlensing, imaging, timing) on exoplanets.org. We also
added some new fields (e.g. the secondary eclipse depths), removed
obsolete fields, and revised some fields as necessary.

@@

Make sure to mention: data are available at exoplanets.org; KOIs are
 included.  ZZZ Also mention the number of confirmed planets? and
 maybe the scope of the EOD (what are in our database)

@@

%------------------------------------------------------------------------------
% Figure: single planet page
\begin{figure}[!htb]
\centering
\includegraphics[width=\textwidth]{../fig/mass-per-interactive.eps}
\caption{ZZZ will change to mass-SEP plot once KOIs have SEP ZZZ
  An example plot produced by the interactive plotting tools of
  EDE on exoplanets.org. The interactive plotting interface is shown
  on the left, with the mass-period plot shown on the right. The
  $x$-axis is planet orbital period in days and $y$-axis is planet
  mass in Earth's mass. The exoplanet samples being plotted are the
  ones in the EOD, including transit planets (blue large dots), RV
  planets (red triangles), and timing planets (magenta squares). The
  KOIs are plotted as black small dots, and their masses are
  calculated using their radii based on mass-radius relations from the
  literature (see Section~\ref{sec:orbit}).}
\label{fig:koi}
\end{figure}
